

\section{\sc Conference Publications}

\onecol
{
  \textbf{N. Tarafdar}, T. Lin, N. Eskandari, D. Lion, A. Leon-Garcia, and P. Chow.
  \textit{Heterogeneous Virtualized Network Function Framework in the Data Center.}
  In 27th International Conference on Field Programmable Logic and Applications (FPL 2017), September 2017. 
}

\onecol
{
  T. Lin, \textbf{N. Tarafdar}, B. Park, P. Chow, and A. Leon-Garcia.
  \textit{Enabling Network Function Virtualization over Heterogeneous Resources.}
  In The 19th Asia-Pacific Network Operations and Management Symposium (APNOMS2017), Seoul, South Korea, September 2017. 
}


\onecol
{
    \textbf{N. Tarafdar}, T. Lin, E. Fukuda, H. Bannazadeh, A. Leon-Garcia, and P. Chow. 
  \textit{Enabling Flexible Network FPGA Clusters in a Heterogeneous Cloud Data Center.}
  In International Symposium on Field-Programmable Gate Arrays (FPGA). ACM, February 2017. 
}

\onecol
{
  S. Byma, \textbf{N. Tarafdar}, T. Xu, H. Bannazadeh, A. Leon-Garcia, and P. Chow. 
  \textit{Expanding OpenFlow Capabilities with Virtualized Reconfigurable Hardware.}
  In International Symposium on Field-Programmable Gate Arrays (FPGA). ACM, February 2015.
}

\onecol
{
    M. Sadoghi, R. Javed, \textbf{N. Tarafdar}, H. Singh, R. Palaniappan, H.A Jacobsen.
  \textit{Multi-query stream processing on FPGAs.}
  In International Conference on Data Engineering (ICDE). IEEE, 2012.
}

\section{\sc Journal Publications}

\onecol
{
  \textbf{N. Tarafdar}, N. Eskandari, V. Sharma, C. Lo, and P. Chow. 
  \textit{Galapagos: A Full Stack Approach to FPGA Integration in the Cloud.}
  In IEEE Micro Special Issue: Hardware Acceleration, 2018.
  TO APPEAR
}


\onecol
{
  \textbf{N. Tarafdar}, N. Eskandari, T. Lin, and P. Chow. 
  \textit{Designing for FPGAs in the Cloud.}
  In IEEE Design \& Test, 35(1):23-29, February 2018.
}


\section{\sc Book Chapters}

\onecol
{
    \textbf{N. Tarafdar}, T. Lin, D. Ly-Ma, D. Rozkho, A. Leon-Garcia, and P. Chow.
    \textit{Building the Infrastructure for Deploying FPGAs in the Cloud.}
    In Hardware Accelerators in Data Centers, chapter 2, pages 9-33, Springer, 2018.
}



\section{\sc Workshop Publications}

\onecol
{
  E. Fukuda, \textbf{N. Tarafdar}, I.C Chen, and P. Chow.
  \textit{Distributed Stream Processing Platform for CPU-FPGA Heterogeneous Data Centers.}
  In Summer United Workshops on Parallel, Distributed and Cooperative Processing (SWoPP), page 5 pages, July 2017.
}

\onecol
{
  E. Fukuda, \textbf{N. Tarafdar}, and P. Chow.
  \textit{Accelerating Apache Drill with FPGA.}
  Apache: Big Data North America, May 2016.
}


\section{\sc Poster Presentations}


\onecol
{
    \textbf{N. Tarafdar}, N. Eskandari, and P. Chow.
    \textit{Galapagos: A Full Stack Approach to FPGA Integration in the Cloud.}
    In Xilinx Developer's Forum (XDF), San Jose, October 2018. 
}



\onecol
{
    \textbf{N. Tarafdar}, T. Lin, H. Bannazadeh, A. Leon-Garcia, and P. Chow.
    \textit{Heterogeneous Virtualized Network Function Chaining in the Data Center.}
    In IEEE Symposium on Field-Programmable Custom Computing Machines (FCCM'17) Demo Night, May 2017. 
}


\onecol
{
    \textbf{N. Tarafdar}, E. Fukuda, J. Chen, and P. Chow.
    \textit{Heterogeneous Virtualized Network Function Chaining in the Data Center.}
    In IEEE Symposium on Field-Programmable Custom Computing Machines (FCCM'17) Demo Night, May 2017. 
}

\onecol
{
    E. Fukuda, \textbf{N. Tarafdar}, and P. Chow.
    \textit{Organizing FPGAs in the Cloud for Distributed Applications.}
    2016 SAVI AGM poster presentation, July 2016. 
}


\onecol
{
    \textbf{N. Tarafdar}, R. Pavone, K. Yuan, E. Fukuda, T. Lin, H. Bannazadeh, A. Leon-Garcia, and P. Chow. 
    \textit{OpenCLoud: A Virtualized Heterogeneous Platform.} 
    The CMC Microsystems 2015 Annual Symposium TEXPO Demonstration, September 2015. 
}

\onecol
{
    Stuart Byma, \textbf{N. Tarafdar}, T. Xu, H. Bannazadeh, A. Leon-Garcia, and P. Chow.
    \textit{Expanding OpenFlow Capabilities with Virtualized Reconfigurable Hardware.}
    2015 SAVI AGM poster presentation, July 2015
}


\onecol
{
    E. Fukuda, \textbf{N. Tarafdar}, and P. Chow.
    \textit{Interactive Large-scale Data Analysis on Virtual FPGAs in the Cloud.}
    2015 SAVI AGM poster presentation, July 2015. 

}


