\pagebreak
\section{\sc Professional Development}

\multicell{\bf Teaching in Higher Education}{2015}
{One semester course}{ }
{
  Learned more about teaching theories and styles and was observed by peers while teaching a tutorial on Computer Architecture.
  Developed a course syllabus for a fictitious course.
}

\multicell{\bf Teaching Engineering in Higher Education}{2015}
{\em One semester course}{ }
{
  Studied concepts and research on curriculum, teaching, and learning in engineering education.
}

\multicell{\bf Prospective Professors in Training}{2014-2015}
{\em Thirteen Seminars, One semester course}{ }
{
  Began preparations for becoming a professor in academia and prepared an academic dossier.
}

\multicell{\bf Mini-MBA}{2015}
{\em Ten Classes}{ }
{
  Gained an understanding of fundamental business concepts and participated a case competition.
}

\multicell{\bf Oral Presentation Skills}{2014}
{\em Five Classes}{ }
{
  Examined presentation structure and the use of visual aids.
  Exchanged feedback with peers.
}

\multicell{\bf Prewriting Strategies for Developing and Organizing Your Ideas}{2014}
{\em Four Classes}{ }
{
  Learned several new strategies for developing and organizing ideas before the writing process.
}

\multicell{\bf NSERC Proposal Workshop}{2014}
{\em Three Classes}{ }
{
  Examined features of good and bad proposal writing, and exchanged feedback with peers.
}

\multicell{\bf Teaching Fundamentals Certificate}{2012-2013}
{\em Six Workshops}{ }
{
  Improved my teaching skills with workshops on pedagogy, research, academic integrity, and students in difficulty.
}
