\section{\sc Teaching Experience}

\multicell{\textbf{Engineering Communication and Design}}{Teaching Assistant}
{\textit{APS111, APS112, APS112T}}{\textit{1st Year Undergraduates, T-Program}}
{
  Facilitated tutorials for group projects with a focus on the engineering design process including how to: define the problem, develop solutions, and objectively compare designs.
  Taught the fundamentals of the design process in the Fall semester (APS111), providing feedback on written work and group dynamics.
  Continued to provide feedback and refine fundamentals in the Winter Semester (APS112) where students worked on a client-facing project.
  Also participated in the summer-session for students who were struggling with their course load (i.e., T-Program, APS112T).
}

\multicell{\textbf{Computer Programming}}{Teaching Assistant}
{\textit{APS105, APS105T, APS106T, ECE244, ECE297}}{\textit{1st \& 2nd Year Undergraduates, T-Program}}
{
  Taught computer programming using the C (APS105, APS105T, APS106T) and C++ languages (ECE244, ECE297).
  Fundamental topics for both C and C++ included data structures, recursion, sorting, input/output, memory management on the stack and heap.
  Additional C++ topics included value versus reference semantics and object-oriented programming.
  The fundamentals learned were applied in a design project (ECE297), where I mentored student groups in implementing an application similar to Google Maps.
  The majority of teaching took place in tutorials (10-80 students) and computer labs.
  \\
  \\
  In addition to tutorials and labs, I have also delivered lectures and developed course materials.
  For APS105, I delivered the 2013 Exam Jam review session.
  For ECE244, I delivered two lectures on recursion using an in-depth maze example with a step-by-step visualization of the maze traversal.
  For ECE297, I proposed, developed, and delivered optional tutorials on software design.
}

\multicell{\textbf{Computer Organization \& Architecture}}{Teaching Assistant}
{\textit{ECE352, ECE552}}{\textit{3rd \& 4th Year Undergraduates, Graduates}}
{
  Supervised and helped students implement a simple von Neumann processor using verilog in a computer lab setting (ECE352).
  Also taught computer architecture concepts (e.g., caches, pipelining, register renaming, prefetching) in the lab.
  Delivered tutorials on Amdahl's Law, quantitative analysis, cache coherence, and memory consistency.
}

